Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-12 tex/MesnardoBarba2019.tex
Try to connect snake simus to overall cost

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)

>>>>

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately see how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spent a total of $20,614$ USD to run CFD simulations, including a couple dozens of snake simulations.
(The output of those simulations are now being processed to further analyze the complex flow dynamics generated behind the snake model.)
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).
(Note that with 3-year-reserved instances, the two- and three-dimensional snake simulations would have only cost $24.6$ and $478.1$ USD, respectively.)
